### 2014-01-22 Draft/introduction.tex
Changed technique->approach in Intro

%Strike out ``To address the aforementioned issue''
We propose a novel approach to infer temporal usage constraints from natural language text of API documents. We propose new techniques that apply Natural Language Processing (NLP) on natural language text API documents to automatically infer temporal usage constraints. 
%In particular, we focus on specific type of constraints namely temporal constraints.
A generic temporal relation is defined as \textit{an interpropositional relation that communicates the simultaneity or ordering in time of events or states.}
In terms of API method invocations, we interpret temporal relationships as \textit{`the allowed sequence of invocations of methods'}.
For example, consider the following statement in \amazonAPI\ ``You must initiate a multipart upload before you can upload any part.''
This statement can be interpreted as multipart-upload method must be invoked before invoking any part-upload method in the API.

@@

% Combine first two sentences
% In contrast, temporal constraints are beyond these parameter constraints. may be use difficult to express using parameter constraints
% Amazon S3 is popularly used web service for simple cloud based storage
Existing approaches focus in inferring method pre-post conditions~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} in terms of parameter constraints either using static or dynamic analysis techniques.
Furthermore, there is a class of NLP based approaches~\cite{pandita12:inferring, wu2013inferring} that infer constraints from API documents.
However, similar to static and dynamic analysis techniques these approaches focus on parameter constraints as well.  
In contrast, temporal constraints are beyond these parameter constraints.
Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods.

@@

Our proposed techniques address the following challenges to infer temporal constraints automatically from natural language text.
First, relying just on type information will result in a incomplete list of temporal constraints. 
Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse
for a strongly typed language.
The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}.
Our proposed approach extends the existing techniques to address the challenge.

>>>>

%Strike out ``To address the aforementioned issue''
We propose a novel approach to infer temporal usage constraints from natural language text of API documents. We propose a new approach that apply Natural Language Processing (NLP) on natural language text API documents to automatically infer temporal usage constraints. 
%In particular, we focus on specific type of constraints namely temporal constraints.
A generic temporal relation is defined as \textit{an interpropositional relation that communicates the simultaneity or ordering in time of events or states.}
In terms of API method invocations, we interpret temporal relationships as \textit{`the allowed sequence of invocations of methods'}.
For example, consider the following statement in \amazonAPI\ ``You must initiate a multipart upload before you can upload any part.''
This statement can be interpreted as multipart-upload method must be invoked before invoking any part-upload method in the API.

@@

% Combine first two sentences
% In contrast, temporal constraints are beyond these parameter constraints. may be use difficult to express using parameter constraints
% Amazon S3 is popularly used web service for simple cloud based storage
Existing approaches focus in inferring method pre-post conditions~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} in terms of parameter constraints either using static or dynamic analysis techniques.
Furthermore, there is a class of NLP based approaches~\cite{pandita12:inferring, wu2013inferring} that infer constraints from API documents.
However, similar to static and dynamic analysis techniques, these approaches focus on parameter constraints as well.  
In contrast, temporal constraints are beyond these parameter constraints.
Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods.

@@

Our proposed approach address the following challenges to infer temporal constraints automatically from natural language text.
First, relying just on type information will result in a incomplete list of temporal constraints. 
Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse
for a strongly typed language.
The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}.
Our proposed approach extends the existing approaches to address the challenge.
